---
title: "p8105_HW_Joseph Kim"
author: "joseph Kim"
date: "10/9/2021"
output: github_document
---

##### Homework 2: Data Wrangling 

```{r setup}
library(tidyverse)
library(readxl)
library(dplyr)
```

## Read in Excel (Import dataset and datacleaning)

```{r}

trashwheel_df=
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx", sheet = "Mr. Trash Wheel", range="A2:N535") %>%   
  janitor::clean_names() %>% 
  na.omit(dumpster) %>% 
  mutate(sports_balls=round(sports_balls,0)) 

```


```{r}

precipitation2018= 
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx", sheet = "2018 Precipitation", range = "A2:B14") %>% 
  janitor::clean_names() %>%
  na.omit() %>%
  mutate(year="2018") 
  
```


```{r}
precipitation2019= 
  read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx", sheet = "2019 Precipitation", range = "A2:B14") %>% 
  janitor::clean_names() %>%
  na.omit() %>%
  mutate(year="2019") 
```


```{r}
totalprecipitation2018_2019 = 
  rbind(precipitation2018, precipitation2019) %>%
  mutate(month = month.name[month])
```

Make sure to write the paragraph here.


### Problem 2: 

```{r}
pols_month = 
  read_csv("./data/pols-month.csv") %>%
  janitor::clean_names() %>%
  separate(mon, c("year","month","day"), "-") %>%
  mutate(month = as.integer(month), year = as.integer(year)) %>%
  mutate(month = month.name[month]) %>%
  mutate(president = ifelse(prez_gop == 0,"dem","gop")) %>%
  select(-prez_dem, -prez_gop, -day)

snp_df = 
  read_csv("./data/snp.csv") %>%
  janitor::clean_names() %>%
  separate(date, c("year","month", "day"), "/") %>%
  mutate(month = as.integer(month), year = as.integer(year)) %>%
  mutate(month = month.name[month], year= year + 2000) %>%
  arrange(year, month)

unemployment_df = 
  read_csv("./data/unemployment.csv") %>%
  pivot_longer(
    2:13,
    names_to = "month",
    values_to = "unemployment_level"
  ) %>%
  mutate(month = match(month, month.abb)) %>%
  mutate(month = month.name[month]) %>%
  janitor::clean_names() %>%
  arrange(year,month) %>% 
  mutate(year = as.integer(year))

snp_pols_merge = 
  left_join(snp_df, pols_month, by=c("year", "month"))

complete_merge = 
  left_join(snp_pols_merge, unemployment_df, by=c("year", "month"))
  
```
Write a short paragraph about these datasets. Explain briefly what each dataset contained, and describe the resulting dataset (e.g. give the dimension, range of years, and names of key variables).


```{r}
babyname_data =  
  read_csv("./data/Popular_Baby_Names.csv") %>%
  janitor::clean_names() %>%
  mutate(ethnicity = ifelse(ethnicity=="ASIAN AND PACI", "ASIAN AND PACIFIC ISLANDER", ethnicity)) %>%
  mutate(ethnicity = ifelse(ethnicity=="WHITE NON HISP", "WHITE NON HISPANIC", ethnicity)) %>%
  mutate(ethnicity = ifelse(ethnicity=="BLACK NON HISP", "BLACK NON HISPANIC", ethnicity)) %>%
  distinct()
  
